\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 coqimpl.tex
changes of wording: equality -> comp behavior

The command \lsti{FInductive tm : Set += tm_fix : }\dadada~in family
\lsti{STLCFix} is again translated to a module type \lsti{STLCFix\_tm} (\cref{fig:stlcfix-compiled}).
It includes all the names declared by \lsti{STLC\_tm}
via command \lsti!Include STLC\_tm(self)!,
and additionally declares
the new constructor \lsti{tm_fix} and related equalities.

@@

An \lsti{FRecursion} definition is translated in two parts:
first a module containing the definitions of all the case handlers,
and then a module type declaring the existence of the recursive function as well as
its propositional equalities.\EDJ{Simiarly, here I think using ``computational behaviour'' is more accurate than using the word ``prop eq''}

@@

Upon \lsti{End}~\lsti{subst}, a module type named \lsti{STLC\_subst} is generated.
%
As discussed in \cref{sec:latebind}, \lsti{subst} can be further bound,
% \EDJ{If we don't allow further binding case handler(mentioned in your last reply), how do the user further bind the subst? I mean in the surface syntax}\YZreply{The position is that individual case handlers cannot be further bound, but the recursive function itself can be further bound by acquiring new case handlers.}
so its definition is not exposed to the fields that come after it.
Accordingly, the translation \lsti{STLC\_subst} merely declares the type of \lsti{subst}
and the existence of its propositional equalities, leaving \lsti{subst} undefined
and the equalities unproven.
%
The propositional equalities are stated in terms of the case handlers,
whose definitions \emph{are} available through the \lsti{self} parameter.
So Coq can simplify, for example, \lsti{subst_tm_unit_eq}'s type to
\lsti!\forall x t, self.subst self.tm_unit x t = self.tm_unit!.
The equalities will be included and available for use in the
translations of the subsequent fields through their \lsti{self}
parameters.

@@

The translation of \lsti{FInduction} is similar, except that there is no need to
register propositional equalities, as \lsti{FInduction} proofs are considered opaque.

>>>>

The command \lsti{FInductive tm : Set += tm_fix : }\dadada~in family
\lsti{STLCFix} is again translated to a module type \lsti{STLCFix\_tm} (\cref{fig:stlcfix-compiled}).
It includes all the names declared by \lsti{STLC\_tm}
via command \lsti!Include STLC\_tm(self)!,
and additionally declares \lsti{tm_fix}, a partial recursor, and related equalities.

@@

An \lsti{FRecursion} definition is translated in two parts:
first a module containing the definitions of all the case handlers,
and then a module type declaring the existence of the recursive function as well as
its computational behaviors.

@@

Upon \lsti{End}~\lsti{subst}, a module type named \lsti{STLC\_subst} is generated.
%
As discussed in \cref{sec:latebind}, \lsti{subst} can be further bound,
% \EDJ{If we don't allow further binding case handler(mentioned in your last reply), how do the user further bind the subst? I mean in the surface syntax}\YZreply{The position is that individual case handlers cannot be further bound, but the recursive function itself can be further bound by acquiring new case handlers.}
so its definition is not exposed to the fields that come after it.
Accordingly, the translation \lsti{STLC\_subst} merely declares the type of \lsti{subst}
and the equalities about its computational behaviors, leaving \lsti{subst} undefined
and the equalities unproven.
%
The equalities are stated in terms of the case handlers,
whose definitions \emph{are} available through the \lsti{self} parameter.
So Coq can simplify, for example, the type of \lsti{subst_tm_unit_eq} to
\lsti[basicstyle=\fontsize{8.5}{9},basewidth=.95ex]{\forall x t, self.subst self.tm_unit x t = self.tm_unit}.
These equalities about the computational bahaviors of \lsti{subst}
will be included and available for use in the translations of the
subsequent fields through their \lsti{self} parameters.

@@

The translation of \lsti{FInduction} is similar, except that there is no need to
register computational behaviors, as \lsti{FInduction} proofs are considered opaque.

### 2022-11-10 stlc-compiled.tex
edits
changes of wording: equality -> comp behavior

[@\codecomment{Instantiate \texttt{tm} partial recursor \& its equalities}@]

@@

[@\codecomment{Instantiate \texttt{subst} \& its equalities}@]

@@

[@\codecomment{Instantiate \texttt{ty}, its constructors, partial recusor \& eq.}@] [@\dadada@][@\tanc{c-STLC-d-ty}@][@\tanc{c-STLC-sndcol-start}@][@\innersep@]

@@

\vspace{-12pt}

>>>>

[@\codecomment{Instantiate \texttt{tm} partial recursor \& its computational behaviors}@]

@@

[@\codecomment{Instantiate \texttt{subst} \& its computational behaviors}@]

@@

[@\codecomment{Instantiate \texttt{ty}, its constructors, partial recusor, etc.}@] [@\dadada@][@\tanc{c-STLC-d-ty}@][@\tanc{c-STLC-sndcol-start}@][@\innersep@]

@@

\vspace{-14pt}

### 2022-11-10 stlcfix-compiled.tex
edits
changes of wording: equality -> comp behavior

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Cases\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases
[@\outdent@](self : STLCFix\_subst\_Cases\_Ctx).
Include STLC\_subst\_Cases(self).[@\hfill\codecomment{reuse}@]
Def subst\_tm_fix := [@\dadada@].[@\hfill\codecomment{translation of new case}@]
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_subst\_Cases.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@][@\textls[-30]{STLCFix}@]\_[@\textls[-30]{subst}@]\_[@\textls[-30]{Ctx}@]).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon conclusion of \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@][@\tanc{c-STLCFix-d-tm-start}@]
Inductive tm : Set :=
| tm_unit : tm | tm_var : id -> tm
| tm_abs : id -> tm -> tm | tm_app : tm -> tm -> tm
| tm_fix : id -> tm -> tm.
[@\codecomment{Instantiate \texttt{tm} partial recursors \& their equalities}@] [@\dadada@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\codecomment{Instantiate \texttt{subst} \& its equalities}@]
Def subst := tm_rect _ subst\_tm_unit
subst\_tm_var subst\_tm_abs subst\_tm_app[@\hfill\codecomment{reuse}@]
subst\_tm_fix.
Fact [@\textls[-40]{subst\_tm\_unit\_eq}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.
Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\codecomment{\textls[-10]{Include\;\texttt{ty}, its constructors, partial recursor \& eq.}}@] [@\dadada@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\codecomment{Include/Instantiate other fields of \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
Include STLC\_typesafe.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-typesafe}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

@@

\vspace{-8pt}

@@

\caption{Compilation of family \lsti!STLCFix! (\cref{fig:stlc-mechanized}).}
\label{fig:stlcfix-compiled}
\end{figure}

>>>>

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Cases\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases
[@\outdent@](self : STLCFix\_subst\_Cases\_Ctx).
Include STLC\_subst\_Cases(self).[@\hfill\codecomment{reuse}@]
Def subst\_tm_fix := [@\dadada@].[@\hfill\codecomment{translation of new case}@]
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_subst\_Cases.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@][@\textls[-30]{STLCFix}@]\_[@\textls[-30]{subst}@]\_[@\textls[-30]{Ctx}@]).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon conclusion of \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@][@\tanc{c-STLCFix-d-tm-start}@]
Inductive tm : Set :=
| tm_unit : tm | tm_var : id -> tm
| tm_abs : id -> tm -> tm | tm_app : tm -> tm -> tm
| tm_fix : id -> tm -> tm.
[@\codecomment{Instantiate \texttt{tm} partial recursors \& their comp.\ behaviors}@] [@\dadada@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\codecomment{Instantiate \texttt{subst} \& its computational behaviors}@]
Def subst := tm_rect _ subst\_tm_unit
subst\_tm_var subst\_tm_abs subst\_tm_app[@\hfill\codecomment{reuse}@]
subst\_tm_fix.
Fact [@\textls[-40]{subst\_tm\_unit\_eq}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.
Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\codecomment{\textls[-10]{Include\;\texttt{ty}, its constructors, partial recursor, etc.}}@] [@\dadada@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\codecomment{Include/Instantiate other fields of \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
Include STLC\_typesafe.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-typesafe}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

@@

\vspace{-3pt}

@@

\caption{Compilation of family \lsti!STLCFix! and the final \lsti!Check! command (\cref{fig:stlc-mechanized}).}
\label{fig:stlcfix-compiled}
\end{figure}
